Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-09-08 bckground.tex
Related work review and comment

\ifreview
Comments to address in this section:
\begin{itemize}
	\color{red} 
	\item REVIEWER 2: the topic of other HPC usage models [OCCAM,FRHPC],
	elastic simulation jobs [ELASTICMC], opportunistic HPC usage [ATLASHPC]
	or proxy infrastructure [ACTATLAS,ACTHYDRA] is not discussed.
\end{itemize}
\fi

>>>>

\ifreview
Comments to address in this section:
\begin{itemize}
	\color{red} 
	\item REVIEWER 2: the topic of other HPC usage models [OCCAM,FRHPC],
	elastic simulation jobs [ELASTICMC], opportunistic HPC usage [ATLASHPC]
	or proxy infrastructure [ACTATLAS,ACTHYDRA] is not discussed.\mtnote{I
	looked for these models and found few references to them. All in all, I
	am not seeing how these fit within the background of pilot-enabled
	workload managers.}
\end{itemize}
\fi
